Fully Generalized Compilation

### 2017-03-14 papers/paper.tex
Adds grammar file notes to paper

The simplest non-trivial grammar file is likely the assignment statement:

\verbatim
assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
\end{verbatim}

@@

\verbatim
name: `first_element` `second_element`
\end{verbatim}

@@

\verbatim
an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
Either:
- A subtype parser (i.e `'='`),
- A subtype-type parser (i.e. `identifier self`)
- A type parser (i.e. `identifier **`)
- A link to another grammar element (i.e. `value`)

@@

`@statement import_from | main | ... ` 
`@val identifier ** | string | literal ** | 'None' | 'True' | 'False'`
`@val vector | functioncall | elementaccess | memberaccess | basevalue | parenexpr`
`@args optional sep ',' expression`

\end{verbatim}

>>>>

The simplest non-trivial grammar file is likely the assignment statement:
\begin{lstlisting}
    assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
\end{lstlisting}

@@

\begin{lstlisting}
name: `first_element` `second_element`
\end{lstlisting}

@@

\begin{lstlisting}
an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
Either:
- A subtype parser (i.e `'='`),
- A subtype-type parser (i.e. `identifier self`)
- A type parser (i.e. `identifier **`)
- A link to another grammar element (i.e. `value`)

@@

`@statement import_from | main | ... ` 
`@val identifier ** | string | literal ** | 'None' | 'True' | 'False'`
`@val vector | functioncall | elementaccess | memberaccess | basevalue | parenexpr`
`@args optional sep ',' expression`
\end{lstlisting}
